00-Data-Processing-Example

### 2021-03-12 examples/00-Data-Processing-Example.Rmd
Update data preprocessing

---
title: "00-Data-Processing-Example"
output: html_notebook
---

@@

Save data files:
```{r}
save(population_sobi, file = "population_sobi.RData")
save(sobi_hubs, file = "sobi_hubs.RData")
save(sobi_hubs_original, file = "sobi_hubs_original.RData")
save(sobi_service, file = "sobi_service.RData")
save(ttm_walk, file = "ttm_walk.RData")
save(ttm_walk_o, file = "ttm_walk_original.RData")
```

>>>>

---
title: "00-Data-Processing-Example"
output:
  pdf_document: default
  html_notebook: default
---

@@

Save data files:
```{r}
save(population_sobi, file = "population_sobi.RData")
save(sobi_hubs, file = "sobi_hubs.RData")
save(sobi_hubs_original, file = "sobi_hubs_original.RData")
save(sobi_service, file = "sobi_service.RData")
save(ttm_walk, file = "ttm_walk.RData")
save(ttm_walk_o, file = "ttm_walk_original.RData")
save(hamilton_da_sobi, file = "hamilton_da_sobi.RData")
save(interpolated_pop_clean, file = "interpolated_pop_clean.RData")
```
